\documentclass[12pt,letterpaper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath, amsthm, amssymb, amsfonts, mathrsfs, amscd, fancyheadings}
\pagestyle{fancy}
\usepackage[top=1in, left=1in, right=1in]{geometry}% http://ctan.org/pkg/geometry
\usepackage{lipsum}% http://ctan.org/pkg/lipsum

\def\AA{{\mathbb A}}
\def\BB{{\mathbb B}}
\def\CC{{\mathbb C}}
\def\FF{{\mathbb F}}
\def\GG{{\mathbb G}}
\def\KK{{\mathbb K}}
\def\MM{{\mathbb M}}
\def\NN{{\mathbb N}}
\def\OO{{\mathbb O}}
\def\QQ{{\mathbb Q}}
\def\PP{{\mathbb P}}
\def\QQ{{\mathbb Q}}
\def\RR{{\mathbb R}}
\def\TT{{\mathbb T}}
\def\ZZ{{\mathbb Z}}

\def\Asf{{\mathsf A}}
\def\Bsf{{\mathsf B}}
\def\Esf{{\mathsf E}}
\def\Fsf{{\mathsf F}}
\def\Psf{{\mathsf P}}
\def\Ssf{{\mathsf S}}

\def\hhat{{\hat h}}
\def\Hhat{{\hat H}}

\def\0{{\mathbf 0}}
\def\1{{\mathbf 1}}
\def\a{{\mathbf a}}
\def\b{{\mathbf b}}
\def\c{{\mathbf c}}
\def\e{{\mathbf e}}
\def\h{{\mathbf h}}
\def\r{{\mathbf r}}
\def\w{{\mathbf w}}
\def\x{{\mathbf x}}
\def\y{{\mathbf y}}
\def\z{{\mathbf z}}
\def\Abf{{\mathbf A}}
\def\Bbf{{\mathbf B}}

\def\Acal{{\mathcal A}}
\def\Bcal{{\mathcal B}}
\def\Ccal{{\mathcal C}}
\def\Dcal{{\mathcal D}}
\def\Ecal{{\mathcal E}}
\def\Fcal{{\mathcal F}}
\def\Gcal{{\mathcal G}}
\def\Hcal{{\mathcal H}}
\def\Ical{{\mathcal I}}
\def\Jcal{{\mathcal J}}
\def\Kcal{{\mathcal K}}
\def\Lcal{{\mathcal L}}
\def\Mcal{{\mathcal M}}
\def\Ncal{{\mathcal N}}
\def\Ocal{{\mathcal O}}
\def\Pcal{{\mathcal P}}
\def\Qcal{{\mathcal Q}}
\def\Rcal{{\mathcal R}}
\def\Scal{{\mathcal S}}
\def\Tcal{{\mathcal T}}
\def\Vcal{{\mathcal V}}
\def\Xcal{{\mathcal X}}
\def\Zcal{{\mathcal Z}}

\def\pfrak{{\mathfrak p}}
\def\Gfrak{{\mathfrak G }}
\def\Rfrak{{\mathfrak R }}

\def\Kbar{{\bar K}}
\def\kbar{{\bar k}}
\def\Fbar{{\bar F}}

\def\arch{\mathrm{arch}}
\def\Aut{\mathrm{Aut}}
\def\ch{\mathrm{char}}
\def\Cl{\mathrm{Cl}}
\def\ker{\mathrm{Ker}}
\def\Div{\mathrm{Div}}
\def\diag{\mathrm{diag}}
\def\Perm{\mathrm{Perm}}
\def\diam{\mathrm{diam}}
\def\disc{\mathrm{disc}}
\def\sgn{\mathrm{sgn}}
\def\grad{\mathrm{grad}}
\def\div{\mathrm{div}}
\def\Isom{\mathrm{Isom}}
\def\ns{\mathrm{ns}}
\def\ab{\mathrm{ab}}
\def\s{\mathrm{s}}
\def\Gal{\mathrm{Gal}}
\def\Nor{\mathrm{Nor}}
\def\Sym{\mathrm{Sym}}
\def\sym{\mathrm{sym}}
\def\Rat{\mathrm{Rat}}
\def\Hom{\mathrm{Hom}}
\def\Spec{\mathrm{Spec}}
\def\Vol{\mathrm{Vol}}
\def\PGL{\mathrm{PGL}}
\def\GL{\mathrm{GL}}
\def\tor{\mathrm{tor}}
\def\Pic{\mathrm{Pic}}
\def\PrePer{\mathrm{PrePer}}
\def\Per{\mathrm{Per}}
\def\Crit{\mathrm{Crit}}
\def\Fix{\mathrm{Fix}}
\def\ord{\mathrm{ord}}
\def\ad{\mathrm{ad}}
\def\Res{\mathrm{Res}}
\def\Prep{\mathrm{Prep}}
\def\trace{\mathrm{trace}}
\def\norm{\mathrm{norm}}
\def\Berk{\mathrm{Berk}}
\def\supp{\mathrm{supp}}
\def\st{\mathrm{st}}
\def\im{\mathrm{Im}}
\def\CS{\mathrm{CS}}
\def\min{\mathrm{min}}

\def\GLn{\mathrm{GL_n}}
\def\Frac{\mathrm{Frac}}
\def\uf{\mathrm{uf}}
\def\uc{\mathrm{uc}}
\def\Tw{\mathrm{Twist}}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{prb}{Problem}
\newtheorem{conj}{Conjecture}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}

\theoremstyle{definition}
\newtheorem*{dfn}{Definition}
\newtheorem*{thmdfn}{Theorem/Definition}
\newtheorem*{dfns}{Definitions}
\newtheorem*{rem}{Remark}
\newtheorem{ex}{Example}

\begin{document}

\title{ZK Bootcamp: Day 4 Problem Set}
\author{Brian Justin Stout\footnote{email: bstout.eth@ethermail.io}}
\maketitle

\begin{prb}\label{P1}
Two parts. Part a: Is it true that all odd squares are $\equiv 1\mathrm{ (mod 8)}$? Part b: What about even squares? Are they $\equiv 1\mathrm{ (mod 8)}$?
\end{prb}

Let $a$ be an odd square. Then for an odd number $\alpha$ we have $\alpha^2=a$. Subtract $1$ from both sides and factor $(\alpha+1)(\alpha-1)=b$ and we wish to show $8|b$. Because $\alpha$ is odd both $\alpha+1$ and $\alpha-1$ are both even. We claim that for any $\alpha$ odd it is true that $\alpha+1$ or $\alpha-1$ is divisible by $4$ and hence all even squares are congruent to $1\mathrm{ (mod 8)}$. We proceed inducively. If $\alpha=3$, then $\alpha+1$ is divisible by $4$. Suppose the result is true for the $n^{th}$ odd number. Arguing by symmetry, assume that $\alpha+1$ is divisible by $4$. Then the next odd number is $\alpha+2$. But then $(\alpha+2)-1=\alpha+1$ which is divisible by $4$.

If $a$ is an even square, we claim $a = 0 \mathrm{ (mod 8)}$ or $a = 4 \mathrm{ (mod 8)}$. Clearly $4=2^2=4\mathrm{ (mod 8)}$ and $16=4^2=0\mathrm{ (mod 8)}$. Assume that $(2k)^2$ is congruent to $0$ or $4$ modulo $8$. Then the next even square is $(2(k+1))^2$ which is congruent to $4(k^2+2k+1)=(4k^2+8k+4)=4k^2+4\mathrm{ (mod 8)}$, which is either $0$ or $4$ depending on the last even square.

\begin{prb}\label{P2}
Try out the vanity bitcoin address example at asecurity or for Ethereum.
\end{prb}

I started running an in-browser vanity address generator to find an address with ``brian" at the beginning. I started running on 4 threads at 12:56pm EST. At 2 hours later I have not found my vanity address and had about 1\% chance so far of finding it.

\begin{prb}\label{P3}
What what do you understand by (a) $O(n)$, (b) $O(1)$, and (c) $O(\log(n))$? For a proof size, which of these would you want?
\end{prb}
The terms $O(n), O(1),\mathrm{ and } O(\log(n))$ represent complexity classes of algorithms. They mean that for an algorithm the number of computations on an input of size $n$ grows approximately like $n$, constant, or $\log(n)$. It does not mean that the algorithm uses exactly this number of computations every time, just that the worst case, dominant term is that function, respectively. $O(1)$ means the number of computations is constant size, or doesn't depend on the input size $n$. A proof of size $O(1)$ would be considered very small, because no matter what the statement (large, very large, or extremely large), the proof size is basically the same size.



\end{document}
